---
title: "Class05:Data Visualization"
author: "Jacklyn (PID: A16410001)"
format: pdf
---

# Graphics Systems in R 

There are many graphics systems in R for making plots and figures. 

We have already played a little with **"base R"** graphics and the 'plot()' function. 

Today we will start learning about a popular graphics package called 'ggplot2()'.

This is an add on package - i.e. we need to install it. I install it (like I install any package) with the 'install.packages()' function. 


```{r}
plot(cars)
```

Before I can use the functions from a package I have to load up the package from my "library". We use the 'library(ggplot2)' command to load it up 

```{r}
library(ggplot2)
ggplot(cars)
```

Every ggplot is made up of at least 3 things: 
- data (the number etc. that will fo into your plot)
- aes (how the columns of data map to the plot aesthetics)
- geoms (how the plot actually looks, points, bars, lines, etc. )

```{r}
ggplot(cars) + 
  aes(x=speed, y=dist) + 
  geom_point()
```

For simple plots ggplot is more verbose - it takes more code - than base R plot.


Add some more layers to you ggplot:

```{r}
ggplot(cars) + 
  aes(x=speed, y=dist) + 
  geom_point() +
  geom_line() +
  geom_smooth(method="lm" , color="pink") +
  labs(title="Stopping Distance of Old Cars", subtitle = "A Silly Example Plot") 
  
```


# Gene Expression Changes Upon Drug Treatment  


```{r}
url <- "https://bioboot.github.io/bimm143_S20/class-material/up_down_expression.txt"
genes <- read.delim(url)
head(genes)
```


```{r}
ggplot(genes)+
  aes(x=Condition1, y=Condition2, col=State)+
  geom_point()
  
```


```{r}
p <- ggplot(genes)+
  aes(x=Condition1, y=Condition2, col=State)+
  geom_point()
```


```{r}
p + scale_color_manual (values=c("blue", "gray", "red"))
```


```{r}
p + scale_color_manual (values=c("blue", "gray", "red"))+
  labs(title="Gene Expresion Changes Upon Drug Treatment",
       x="Control (No Drug)", 
       y="Drug Treatment")
```


# Gapminder 


gapminder_2007


```{r}
library (gapminder)
library(dplyr)

gapminder_2007 <- gapminder %>% filter(year==2007)
```


plotting 


```{r}
ggplot(gapminder_2007)+
  aes(x=gdpPercap, y=lifeExp)+
  geom_point()
```


add "alpha=" to 'geom_point()' to make points more transparent 


```{r}
ggplot(gapminder_2007)+
  aes(x=gdpPercap, y=lifeExp)+
  geom_point(alpha=0.5)
```


Adding Colors with 'aes()' function 


```{r}
ggplot(gapminder_2007)+
  aes(x=gdpPercap, y=lifeExp, color=continent, size=pop)+
  geom_point(alpha=0.5)
```


Scaling Information 


```{r}
ggplot(gapminder_2007)+
  aes(x=gdpPercap, y=lifeExp, color=continent, size=pop)+
  geom_point(alpha=0.5)+
  scale_size_area(max_size=10)
```


gapminder_1957


```{r}
gapminder_1957 <- gapminder %>% filter(year==1957)
```


plotting 


```{r}
ggplot(gapminder_1957)+
  aes(x=gdpPercap, y=lifeExp, color=continent, size=pop)+
  geom_point(alpha=0.7)+
  scale_size_area(max_size=15)
```


Plotting both 2007 and 1957 


```{r}
gapminder_1957 <- gapminder %>% filter(year==1957 | year==2007)

ggplot(gapminder_1957)+
  aes(x=gdpPercap, y=lifeExp, color=continent, size=pop)+
  geom_point(alpha=0.7)+
  scale_size_area(max_size=10)+
  facet_wrap(~year)

```

