---
title: "06_Class6_HW"
author: Jacklyn Jung 
date: 01.28.2024
format: pdf
editor: visual
---

## R Functions 

```{r}
# (A. Can you improve this analysis code?
df <- data.frame(a=1:10, b=seq(200,400,length=10),c=11:20,d=NA)
df$a <- (df$a - min(df$a)) / (max(df$a) - min(df$a))
df$b <- (df$b - min(df$a)) / (max(df$b) - min(df$b)) 
df$c <- (df$c - min(df$c)) / (max(df$c) - min(df$c))
df$d <- (df$d - min(df$d)) / (max(df$a) - min(df$d))
df$a
df$b
df$c
df$d
```

```{r}
df <- data.frame(a=1:10, b=seq(200,400,length=10),c=11:20,d=NA)
normalize_column <- function(column) {
  return((column - min(column, na.rm = TRUE)) / (max(column, na.rm=TRUE) - min(column, na.rm=TRUE)))
}
```


```{r}
normalize_column(df$a)
normalize_column(df$b)
normalize_column(df$c)
normalize_column(df$d)
```
```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
```


```{r}
# Can you improve this analysis code?
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```
```

Q1. What type of object is returned from the read.pdb() function?

- The read.pdb() function returns class of protein structure data in PDB format (three-dimensional structures)

Q2. What does the trim.pdb() function do?

- The trim.pdb() function helps to specify protein data structure that is returned. 

Q3. What input parameter would turn off the marginal black and grey rectangles in the plots and what do they represent in this case?

- We would turn off the margin input parameter to remove the marginal black and grey rectangles in the plot. We can add the mar=FALSE argument to the function. 

Q4. What would be a better plot to compare across the different proteins? 

- ggplot2 might be a better plot to compare across different proteins with more aesthetically pleasing features. 

Q5. Which proteins are more similar to each other in their B-factor trends. How could you quantify this? 

